

<!-- [![Travis build status](https://travis-ci.org/chuvanan/metrics.svg?branch=master)](https://travis-ci.org/chuvanan/metrics) -->
<!-- [![Codecov test coverage](https://codecov.io/gh/chuvanan/metrics/branch/master/graph/badge.svg)](https://codecov.io/gh/chuvanan/metrics?branch=master) -->
<!-- [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental) -->

## metrics

### Why yet another R metrics package?

Because I believe there's still a niche for an R package that have all the
following traits in one place:

- *Simple*

- *Consistent interface*

- *Well-documented*

- *Well-tested*

- *Accurate and fast*

Why do I think so? During my evaluation work on a machine learning project, I
haven't found any single R package that is on a par with scikit-learn's
`metrics` module in term of coverage, ease of use, throughout testing and
documentation richness. For instance,

* The two major frameworks for doing machine learning in R are `caret` and
  `mlr(3)`. The next generation of `caret` is `tinymodels` of which `parnship`
  is the main package for performance metrics.

* `pROC`, `precrec`

* `InformationValue`

* `Metrics`, `ModelMetrics`

I'm not saying that these packages are terrible. However, they're often created
for a very specific use case(s) with highly varied quality and design.

### Overview of `metrics`

#### Installation

Install the stable version of `metrics` from CRAN:

```{r, eval=FALSE}
install.packages("metrics")
```

Or install the development version from Github with:

```{r, eval=FALSE}
devtools::install_github("chuvanan/metrics")
```

#### Getting started

All `metrics` functions share the same interface: `mtr_fun(actual, predicted)`
which is applicable to both classification and regression settings. The design
and rationale behind the API:

* `mtr_` is the short form of **m**e**tr**ics. As in `stringr` package,
  `metrics` uses the prefix to provide consistent naming that makes it easy to
  type with autocompletion in RStudio or Emacs's ESS.

* `_fun` is the name of performance metrics. The package declares verbosely
  which measure is going to be used. For a full list of evaluation metrics,
  please see TODO.

* `metrics` prefers convention over configuration. Argument `actual`, in context
  of classification tasks, stricly accepts binary values `0` and `1` where the
  former is coded as negative class and the later is positive one.

Here's a quick example of `metrics` in action:

```{r}
library(metrics)

## simulate sample data set
set.seed(123)
preds <- runif(1000)
truth <- round(preds)
preds[sample(1000, 300)] <- runif(300) # noise

## overall accuracy
mtr_accuracy(truth, preds)              # default threshold is 0.5

## precision
mtr_precision(truth, preds)

## recall
mtr_recall(truth, preds)

## AUROC
mtr_auc_roc(truth, preds)
```
